---
monofont: Fira Code Light
echo: true
code-fold: true
---

# Conversion paths

In this section I plan to look at the conversion paths data export into more detail. The one big question waiting to be asked and answered with this kind of file export is - building a Markov model on the conversion paths and investigating the resulting network:

-   how does it compare against the simpler heuristics like last touch / first touch ?
    -   here in particular it would be interesting to compare against the last touch as that would actually give us a eye-to-eye comparison of these 2 types of attribution models
    -   given that I have already seen the last-non-direct attributed view on the data from the `country_medium.csv` file, I am curious how would the `referral` medium perform in this view
-   what do the Removal Effects say i.e. according to the Markov model - what % of the conversions would not have happened - had we removed a certain medium
    -   here also in particular it would be interesting to see how do the main contributors from the country/medium analysis fare against each other i.e. how do `referral, (none), organic, cpc` do in terms of their removal effects ? are some over-/under- valued ?

While these are the major points I expect to come out of this section, one other interesting thing could be

-   check the distribution of the conversion path lenghts; what is the most usual length of touchpoints that customers go through before converting ?

The first section explores a bit the data and does some cleaning - feel free to jump to the more interesting parts:

-   A [look](#distribution-path-lengths) at the average number of steps it takes for a client to make a conversion on the client's website
-   Exploring the results from the Markov model, the [transition probabilities](#transition-matrix-conclusions), the [removal effects](#removal-effects) and a [comparison](#heuristic-vs-markov) of heuristic vs. markov model conversion attribution results

# Data exploration

```{r}
#| label: setup
#| echo: false
#| warning: false
#| message: false
library("here")
library("fs")
library("DT")
library("glue")
library("janitor")
library("scales")
library("tidyverse")

data_dir <- "data"
file_name <- "conversion_paths.csv"

conv_paths_raw <-
  read_csv(path_join(c(here(), data_dir, file_name))) |>
  clean_names()
```

## Conversions are all 1s ?

Are all conversions a single `1` or is there variety in the data ?

```{r}
#| label: explore-conversions-1
#| warning: false
#| message: false
conv_paths_raw |>
  select(-medium_path) |> 
  head(10) |> 
  datatable(options = list(dom = "t"))
```

Seems like most of conv. are 1s but perhaps there are some other values ?

```{r}
#| label: explore-conversions-2
summary(conv_paths_raw$conversions)
```

The summary shows that most are 1s but there are other values at the right tail end of the distribution. There are no 0 conversions, which is good.

I can convert them to integer numbers.

```{r}
#| label: convert-conversions-to-integers
conv_paths <- conv_paths_raw |>
  mutate(conversions = as.integer(conversions))
```

## Value always in EUR ?

Separate the EUR from the numeric value and split them separately to check how they look like.

```{r}
#| label: explore-values-1
conv_paths <- conv_paths |>
  mutate(
    value_splits = str_split(value, " ", n = 2),
    currency = map_chr(value_splits, first),
    value = {
      map_chr(value_splits, nth, n = 2) |>
        str_remove_all(",") |>
        parse_number()
    },
    value_splits = NULL
  )
```

Is the currency of the value always in EUR ?

```{r}
#| label: explore-values-2
conv_paths |> count(currency)
```

Yes, great I can safely drop this.

```{r}
#| label: explore-values-3
conv_paths <- conv_paths |> select(-currency)
```

How does `value` look like ?

```{r}
#| label: explore-values-4-a
summary(conv_paths$value)
```

The summary shows that value does have `0`s , half of the data values are `<= 229` and the right end of the tail looks like it is quite long / heavy.

How does this right-end of the tail look like ?

```{r}
#| label: explore-values-4-b
quantile(conv_paths$value, seq(0.9, 1, 0.01)) |> comma()
```

Looks like we have suuuper heavy tail with some extreme values in the top percentiles.

I would like to see the top 10 medium paths ordered by descending conversion value.

```{r}
#| label: explore-values-5
conv_paths |>
  slice_max(order_by = value, n = 10) |> 
  datatable(options = list(dom = "t"))
```

It looks like there are some "power" paths that provide massive part of the conversions / value.

Given the insights from the country/medium analysis - it's not surprising that the single `referral` touchpoint is right at the top - with other paths where `referral` plays a role being also in the top 10.

Seeing also `(none)` and `cpc` in the top 10 makes me more curious about the Markov Model - I expect them to gain on importance in that overall view (as compared to the last non-direct view of the country/medium file).

One more thing I would like to check is the relationship of `(conversion, value)` pairs.

I will start with a simple scatterplot of their relationship.

```{r}
#| label: explore-values-6
# how do conversions-value pairs look like ?
ggplot(conv_paths, aes(conversions, value)) + geom_point()
```

Not entirely sure what to think of this big hole in the middle, at first glance it looks bit unrealistic ?

Wondering if some scale-changes would show something ? Will try to log both axis

```{r}
#| label: explore-values-7
ggplot(conv_paths, aes(conversions, value)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10()
```

Hm, ok ... what catches the attention is the last warning about infinite values. This indicates that there are `0` value conversions ?

```{r}
#| label: explore-values-8
conv_paths |>
  filter(value < 1) |> 
  datatable(options = list(dom = "t"))
```

Yes that is the case indeed ... not sure if this is a "hiccup" in the data / export ?

What percentage of the rows have `0` value ?

```{r}
#| label: explore-values-9
conv_paths |>
  count(value == 0) |>
  mutate(perc = n / sum(n))
```

about 4% of the rows are `0` value. How about in terms of conversions - what % of the conversions (which are all `>= 1`) have `0` value ?

```{r}
#| label: explore-values-10
conv_paths |>
  group_by(value == 0) |>
  summarise(n = sum(conversions)) |>
  mutate(perc = n / sum(n))
```

Since it's only 4% of the data and 0.12% in terms of conversions then i think it's safe to simply remove these rows. It does not make sense to me to have `conversion = 1 & value = 0` - perhaps it's a cancellation ? In any case it shouldn't cause any problems I assume.

```{r}
#| label: explore-values-11
conv_paths <- conv_paths |> filter(value > 0)
```

## What are all possible mediums represented ?

Last thing i would like to check all the different mediums reprensented in this data export

```{r}
#| label: explore-mediums-1
mediums <- conv_paths |>
  select(medium_path) |>
  separate_wider_delim(
    medium_path,
    delim = " > ",
    too_few = "align_start",
    names_sep = "_"
  )

mediums |> map(unique)|> flatten_chr() |> unique() |> sort()
```

From a first look it looks like the same mediums as in the country/medium file, nothing super interesting here.

# Distribution of path lenghts {#distribution-path-lengths}

What might be also interesting to look at is the distribution of path lengths and - out of curiosity - i want to check what is the most common first medium touchpoint usually.

Maybe an idea would be to come up with some simple rules for buckets and see if these 2 differ

-   the bulk of the path lenghts distribution would be centered around some value `L` e.g.
-   however - perhaps the bulk of the *value* is brought by another bucket e.g. `L + 10` i.e. the bulk of the conversions are around `L` but they are lower value conversions than bucket `L + 10`

These are some of the questions I expect to perhaps show some interesting things.

## In terms of number of steps

How does the distribution of path lengths look like ?

```{r}
#| label: explore-path-lenghts-1
path_lengths <- conv_paths |>
  mutate(
    path_splits = str_split(medium_path, " > "),
    path_length = map_int(path_splits, length),
    first_touchpoint_medium = map_chr(path_splits, first)
  ) |> 
  select(path_length, first_touchpoint_medium, value)

ggplot(path_lengths, aes(path_length)) + geom_histogram(binwidth = 1)
```

It's heavily right skewed with extremely long path lengths - apparently conversion paths of `> 100` steps are also possible, although very unlikely. I want to zoom in around the peak of the distribution and see where it lies.

```{r}
#| label: explore-path-lenghts-2
#| warning: false
ggplot(path_lengths, aes(path_length)) +
  geom_histogram(binwidth = 1) +
  xlim(0, 50)
```

It is centered somewhere around `7-9.`

How does the right end of the distribution look like ?

```{r}
#| label: explore-path-lenghts-3
quantile(path_lengths$path_length, probs = seq(0.50, 1.00, 0.05))
```

-   half of the conversions take `<= 10` touchpoints to convert
-   90% of the conversions take `<= 26` touchpoints to convert

## In terms of value

In terms of number of steps - the most common paths are 7-9 steps long, but how about in terms of value ? What are the path lengths that bring the most monetary value and are these the same ?

```{r}
#| label: explore-path-lenghts-4
path_lengths |> 
  group_by(path_length) |> 
  summarise(value = sum(value)) |> 
  filter(path_length <= 15) |> 
  ggplot(aes(x = as.factor(path_length), y = value)) +
  geom_col() +
  scale_y_continuous(labels = label_comma(prefix = "€")) +
  labs(
    x = "Path length",
    y = NULL,
    title = "Monetary value brought by the different path lengths"
  ) +
  theme(
    plot.title.position = "plot"
  )
```

It seems like the path length is highly (negatively) correlated with the value it brings i.e. the longer the path - the less value we expect it to bring. I guess this makes sense ? I imagine a highly "unsure" customer that is hesitating and keeps "prolonging" the customer journey vs. a determined or decisive customer whose journey is more focused ( on the other hand i wonder if this is not always the case for every industry and business ?).

What % of the value is brought by path lengths of `<= 10` ?

```{r}
path_lengths |> 
  group_by(path_length) |> 
  summarise(value = sum(value)) |> 
  mutate(
    perc = value / sum(value),
    cumul = cumsum(perc),
    across(c(perc, cumul), percent_format(accuracy = 0.1))
  ) |> 
  datatable()
```

\~95% of the value is already brought by path lengths of `<= 5` !

In any case - this view could be useful in some marketing optimisations i.e. if we would be able to determine the already-existing path length of a customer - then we could increase or decrease our marketing spend in order to nudge the customer or to save some costs (if we would be able to determine the customers whose journey already overstepped e.g. path length of 6 then we could chose to save these costs or re-invest them in remarketing to customers who are still at step 2 or 3 - as we know that small % of the value comes past this threshold).

## Most common first medium

What is the most common first medium ? This one I picked out of curiosity to see how does the usual customer journey starts.

```{r}
#| label: explore-path-lenghts-5
path_lengths |>
  count(first_touchpoint_medium, sort = T) |>
  mutate(perc = percent_format(accuracy = 0.001)(n / sum(n)))
```

Again perhaps unsurprisingly as I saw in the country/medium analysis - `referral` is the 1st touchpoint for people \~45% of the time being the "power" medium drivers of customers - with `(none)` and `cpc` following behind.

Are there any duplicate rows in the data ?

```{r}
#| label: explore-path-lenghts-6
conv_paths$medium_path |> duplicated() |> sum()
```

yes, so this means i have multiple rows with same medium path and different conversions and values, so I need to re-group-and-summarise by medium path the duplicates.

```{r}
#| label: explore-path-lenghts-7
conv_paths <- conv_paths |>
  group_by(medium_path) |>
  summarise(across(c(conversions, value), sum)) |>
  ungroup()
```

At this point I am content with the checks, cleaning and format of the file.

# Markov model

Given such data with conversion paths of customers, we can use it to build a network where each node is a marketing medium and each edge is the probability of going in that direction i.e. having a touchpoint with the node/medium at the start of the edge, followed by a node/medium at the end of the edge. The probabilities of the edges or transitions are estimated from the data.

I would like to fit a order-1 Markov Model to the conversion paths, which would estimate the 1-step probabilities of transitioning through the marketing mediums network.

```{r}
#| label: markov-model-1
#| message: false
#| warning: false
library("ChannelAttribution")

markov_mod <- markov_model(
  conv_paths,
  var_path = "medium_path",
  var_conv = "conversions",
  var_value = "value",
  out_more = T,
  nsim_start = 1000000
)
```

## Transition Matrix

Select only the top 10 to de-clutter the network

```{r}
top_mediums <- markov_mod$result |> 
  slice_max(order_by = total_conversions, n = 11)
```

```{r}
#| label: transition-matrix-prepare-for-plot

# channel index <-> name
channel_index_to_name <- markov_mod$result |>
  as_tibble() |>
  select(channel_name) |>
  rownames_to_column("channel_index") |>
  deframe()


transition_matrix <- markov_mod$transition_matrix |>
  as_tibble() |>
  mutate(
    channel_from = ifelse(
      channel_from %in% c("(start)", "(conversion)"),
      channel_from,
      channel_index_to_name[ channel_from ]
    ),
    channel_to = ifelse(
      channel_to %in% c("(start)", "(conversion)"),
      channel_to,
      channel_index_to_name[ channel_to ]
    )
  ) |> 
  semi_join(
    top_mediums,
    join_by(channel_from == channel_name)
  ) |> 
  group_by(channel_from) |> 
  slice_max(order_by = transition_probability, n = 4, with_ties = F) |> 
  ungroup()
```

### Heatmap

```{r}
transition_matrix |> 
  ggplot(aes(x = channel_from, y = channel_to, fill = transition_probability)) +
  geom_tile() +
  geom_label(
    aes(label = percent_format(accuracy = 0.1)(transition_probability)),
    label.size = NA,
    alpha = 0.5,
    size = 3.4
  ) +
  scale_fill_gradient(
    low = "tomato2",
    high = "olivedrab3",
    na.value = "cornsilk4"
  ) +
  coord_flip() +
  labs(x = "From", y = "To") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
    legend.direction = "horizontal"
  )
```

#### Conclusions from this part {#transition-matrix-conclusions}

*(N.B. the rows do not sum up to 1 because i trimmed some channels with very small transition probabilities in order to keep the network de-cluttered).*

As suspected - quite some interesting and different views on customer conversions from this side.

-   To end up in the `(conversion)` state, the highest transition probability 82.6% is coming from `(none)/direct`. This means that - given that you had a direct click (or visit coming in directly by typing the website) - then the most likely thing that you will do next is to actually convert
    -   Compare this with 68.8% coming from `referral` which seems significantly less and quite in contrast to the country/medium view where `referral` was always dominating the shares
    -   to restate it bit differently
        -   there is a 1 in 1.21 chance that you will convert - if your last click was `(none)/direct`.
        -   there is a 1 in 1.45 chance that you will convert - if your last click was `referral`
        -   so having a `direct` click increases your chances by 20% to convert
-   from an `organic` state - it's more likely that the path continues to a `cpc` or `(none)` than to a `(conversion)`
    -   `organic` is an important middle-step in the customer journey that feeds the other mediums
-   also conversely, crossing a `cpc` paid search touchpoint is most likely coming from an `organic` search
    -   after having organic search click - people do click on paid search ads
    -   thought/wonder - had the website converted them better at the organic search step - there would be no need to pay for the paid search ad, hence optimising the marketing spend ?
-   after `referral` one wold most likely either convert or continue to a `(none)` touch
    -   following the referral click, people either convert or go on to visit the client directly - which probably means that they will most likely convert as the transition direct -\> conversion is the highest
        -   in order to confirm this we need to look at the order-2 markov model and the transition probability of referral -\> direct -\> conversion

### Graph

I found it a bit difficult to find an appropriate graph size and layout in order to be able to easily draw conclusions or see patterns and cliques in the data. It's a pity that it just looks nice but it's not super useful for most practical problems.

```{r}
#| label: static-plot-markov-network
#| warning: false
#| message: false
library("igraph")

top_mediums <- c(
  "(start)",
  "(conversion)",
  "(none)",
  "(not set)",
  "cpc",
  "email",
  "organic",
  "referral"
)

transition_matrix <- transition_matrix |> 
  filter(
    channel_from %in% top_mediums,
    channel_to %in% top_mediums
  )

network <- graph_from_data_frame(d = transition_matrix, directed = T)

V(network)$color <- case_match(
  V(network)$name,
   "(start)"       ~ "darkslategray3",
    "(conversion)" ~ "gold3",
    "(none)"    ~ "darkolivegreen3",
    "email"     ~ "darkolivegreen3",
    "navbar"    ~ "darkolivegreen3",
    "organic"   ~ "darkolivegreen3",
    "referral"  ~ "darkolivegreen3",
    "(not set)" ~ "firebrick2",
    "cpc"       ~ "firebrick2",
    "s-cpm"     ~ "firebrick2"
)

plot(
  network,
  layout = layout_with_fr,
  edge.arrow.size = 0.2,
  edge.curved = F,
  edge.label = percent_format(accuracy = 0.1)(E(network)$transition_probability)
)
```

## Removal Effects {#removal-effects}

It's important to keep in mind here what the removal effects mean. Imagine a linear conversion path

`email -> direct -> conversion`

Both of these channels have 100% removal effect because the conversion would not happen if we remove either of them. That's why the following removal effects do not sum up to 100%.

```{r}
#| label: removal-effects-1
markov_mod$removal_effects |> 
  as_tibble() |>
  filter(removal_effects_conversion_value > 0.0) |> 
  arrange(desc(removal_effects_conversion_value)) |> 
  mutate(across(starts_with("removal_"), percent_format(accuracy = 0.01))) |> 
  datatable()
```

-   `referral` is getting over-valued in the country/medium (last non-direct) attribution model where it has the lion's share of revenue consistently across all countries. even though it's not the same measure - still the effect according to the Markov model is \~60% whereas it used to be more like \~80% in the country/medium view
-   `(none)/direct` is getting under-valued in the country/medium view, being credited there with only like \~8% of the revenue. In this view it is almost on par actually with `referral`
    -   so direct is almost the same value as referral - this is a huge change in value perspective (it is not the same value - but nevertheless direct went from getting \~8% of the value to \~54% of the value)
-   `cpc` seems to be very close in terms of attribution from both views
-   the order is the same but the % attributed value differs (at least for the top 2 mediums)

# Heuristic Model {#heuristic-vs-markov}

```{r}
#| label: heuristic-mod-setup
heuristic_mod <- heuristic_models(
  conv_paths,
  var_path = "medium_path",
  var_conv = "conversions",
  var_value = "value"
)

markov <- markov_mod$result |> 
  rename(
    markov_conversions = total_conversions,
    markov_conversion_value = total_conversion_value
  )

heuristic <- heuristic_mod |>
  rename_with(
    .cols = c(everything(), -channel_name),
    str_remove,
    pattern = "touch_"
  )
```

::: panel-tabset
## All on one

```{r}
top_mediums <- 
  markov_mod$result |> 
  slice_max(order_by = total_conversions, n = 6)

compare_models <- 
  left_join(markov, heuristic, join_by(channel_name)) |> 
  semi_join(top_mediums, join_by(channel_name)) |> 
  select(channel_name, ends_with("conversions")) |> 
  rename_with(
    .cols = c(everything(), -channel_name),
    str_remove,
    pattern = "_conversions"
  ) |> 
  pivot_longer(
    cols = -channel_name,
    names_to = "model",
    values_to = "value"
  ) |> 
  mutate(
    channel_name = fct_reorder(channel_name, value, sum, .desc = T)
  )

compare_models |> 
  ggplot(aes(x = channel_name, y = value, fill = model)) +
  geom_col(position = "dodge") + 
  scale_fill_brewer(palette = "Set1")
```

## Free facets

```{r}
compare_models |> 
  ggplot(aes(x = channel_name, y = value, fill = model)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = label_comma()) +
  #scale_fill_viridis_d(begin = 0.01, end = 0.97) +
  scale_fill_brewer(palette = "Set1") + 
  facet_wrap(~ channel_name, scales = "free") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  labs(
    y = "# Conversions",
    x = NULL
  )
```
:::

-   `referral` is generally less valuable as compared to the heuristic models, although it is practically the same as the last-touch model. It is getting a lot of value in the first-touch model which means it's often quite high in the funnel / customer journey
-   `(none)` is getting much less-valued in the first-touch vs. much more valued in the Markov and last-touch. This indicates that it is quite low in the funnel / customer journey, right at the end towards the conversion moment
    -   it might be confusing why the direct channel got a big jump in attribution when comparing e.g. 8% from the country/medium view whereas here we saw the removal effect of 54%
        -   the fact that `(none)` or `direct` is less valued in the Markov model compared to Last model - while also having 54% removal effect is due to the fact that Markov model *shares* the conversions across the channels responsible for it - but all the channels in a conversion path get 100% removal effect due to the fact that the conversion would not have happened if we remove them all (imagine a linear conversion path with 2 channels and conversions - these both have 100% removal effect while also having 1/2 of the conversion)
-   `organic` is much more valued in the Markov model than in the simpler ones - indicating that it is very instrumental in-between touch for a lot of the conversions
-   same could be said for `email, cpc` although to a lower extent and on lower scale
-   `cpc` seems to be same valued across first-touch and Markov which means it's also probably more high in the conversion funnel
-   `organic` and `email` are much more valueable in reality as the simpler heuristic models can attribute

The one big general takeaway from the whole section here is the importance of testing, comparing and using different models and ways of attributing value to different touchpoints in a journey. None of these models tells the whole truth on their own and it is important to "triangulate" the truth by using various models and ways to inspect the truth.

Moreover - it's further closer to the truth not just different attribution models, but also completely different methods e.g. Attribution Models in addition to Marketing Mix Modelling in addition to Geo/Lift tests. Each and every one can uncover bits of reality and the power lies in combining these in order to measure the effectiveness of marketing.
